Automatic Matching of Bullet Lands

### 2016-01-08 imaging-paper.Rnw
Typo

\subsection{Varying smoothing factor}\label{sec:smoothing}
As mentioned earlier, the algorithm for detecting peaks and valleys depend on the selection of a smoothing window, called the smoothing factor or span. A smoothing factor of $k$ means that the  $k$ closest observations to $x_o$ are considered for a fit for $x_o$. Because surface measurements are recorded at an equidistant resolution (here, of 1.5625$\mu m$), we decided to only consider odd smoothing factors $2k + 1$, which means that the  $k$ observations to the left and right of $x_o$ are considered for a local fit of $x_o$..  For detecting and removing the grooves prior to fitting a loess regression we selected a smoothing factor  of 35, while for detecting the peaks/valleys of the loess residuals a smoothing factor of 25 seems more appropriate. %We can investigate the performance of peak/valley detection across different smoothing factors.

>>>>

\subsection{Varying smoothing factor}\label{sec:smoothing}
As mentioned earlier, the algorithm for detecting peaks and valleys depend on the selection of a smoothing window, called the smoothing factor or span. A smoothing factor of $k$ means that the  $k$ closest observations to $x_o$ are considered for a fit for $x_o$. Because surface measurements are recorded at an equidistant resolution (here, of 1.5625$\mu m$), we decided to only consider odd smoothing factors $2k + 1$, which means that the  $k$ observations to the left and right of $x_o$ are considered for a local fit of $x_o$. For detecting and removing the grooves prior to fitting a loess regression we selected a smoothing factor  of 35, while for detecting the peaks/valleys of the loess residuals a smoothing factor of 25 seems more appropriate. %We can investigate the performance of peak/valley detection across different smoothing factors.
